IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-19 ms.tex
I added a tiny sentence about the reference star, but still haven't figured out which one.

We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J1821+14010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J0835-019 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.

@@

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.

\input{observing_table.tex}

@@

>>>>

We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J0835-019 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.

@@

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - (I think it was 2MASS 18212622+1414064, J=12.58, H=11.97, K=11.82  at a distance of 30.1\arcsec\ or was it 2MASS 18212622+1414064, J=11.25, H=10.91, K=10.85 at a distance of 19.1\arcsec)?
\input{observing_table.tex}

@@

For 2MASS J1821, we
